\documentclass[12pt]{article}
\pagenumbering{gobble}
\linespread{1.2}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage[margin=1in,headheight=1in]{geometry}

\newcommand{\contradiction}{
    \ensuremath{{\Rightarrow\mspace{-2mu}\Leftarrow}}
}

\newcommand{\angleb}[1]{\left\langle#1\right\rangle}
\newcommand{\vertb}[1]{\left\vert#1\right\vert}
\newcommand{\bracks}[1]{\left[#1\right]}
\newcommand{\parns}[1]{\left(#1\right)}

\newcommand{\derv}[2]{\dfrac{d#1}{d#2}}
\newcommand{\e}{\varepsilon}
\newcommand{\di}{\,/\,}

\newcommand{\lm}[1]{\displaystyle\lim_{#1}}

\begin{document}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{Alex Agruso}
\fancyhead[R]{Topology Writing 2}

\normalsize

\begin{itemize}
    \item[1.)] If I were to describe $S^2$ to a two-dimensional being, I would start by having them consider particular circle in the $xy$-plane. If you think of every point on this circle as a portal to another universe that contains its own circle, you can start to think of ways for a two-dimensional being to navigate $S^2$. For example, consider how a two-dimensional being would use the portals to navigate to the pole of the sphere lying on the positive $z$-axis. Find the point on the circle that corresponds to the circle lying on the $yz$-plane. Then, have the being travel through the point to the other circle. Now this being, despite having never perceived a third dimension, has moved from the $xy$-plane to the $yz$-plane, and thus through the third dimension. Expanding this idea to every point on the circle, and definiting a surjection that each point on the circle to a circle that is orthogonal the $xy$-plane. The union of all of these circles would form $S^2$, and for our two-dimensional being, would be fully traversable using the above portal system.

    \item[2.)] The four-dimensional being can use a similar method that was used for the two-dimensional being. Consider every point in $S^2$ as a portal that brings you to another universe containing its own sphere orthogonal to the original. Using these portals, a three-dimensional being would be able to travel to these spheres, and consequently every point in $S^3$. The difference between a three-dimensional and four-dimensional being, however, is the fact that a four-dimensional being can exist in multiple of these other spheres at once, while doing so is impossible for the three-dimensional being
\end{itemize}

\end{document}
