\documentclass[12pt]{article}
\pagenumbering{gobble}
\linespread{1.2}

\setlength{\parskip}{0.15in}%

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage[margin=1in,headheight=1in]{geometry}

\usepackage{tikz}
\usetikzlibrary{arrows.meta}

\newcommand{\contradiction}{
    \ensuremath{{\Rightarrow\mspace{-2mu}\Leftarrow}}
}

% bracket commands
\newcommand{\angleb}[1]{\left\langle#1\right\rangle} % <>
\newcommand{\vertb}[1]{\left\vert#1\right\vert}      % ||
\newcommand{\bracks}[1]{\left[#1\right]}             % []
\newcommand{\braces}[1]{\left\{#1\right\}}           % {}
\newcommand{\parens}[1]{\left(#1\right)}             % ()

% set aliases
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}

\newcommand{\derv}[2]{\dfrac{d#1}{d#2}}
\newcommand{\e}{\varepsilon}
\newcommand{\di}{\,/\,}

\newcommand{\lm}[1]{\displaystyle\lim_{#1}}

\begin{document}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{Alex Agruso}
\fancyhead[R]{Topology Writing 7}

\normalsize

\noindent
In preparation for grad school, I have been studying higher level topics such as elliptic curves and analytic number theory. I am also continuing to work with Dr. Hindes on elliptic curves specifically. Personally, I feel that I learn much faster while working independently or in a small group than I do in larger classes, so I will continue to do this whenever possible.

\noindent
My sleep habits are interesting to say the least.

\noindent
So far, my experiences with the math department here have been almost entirely positive. Apart from a particularly brutal statistics professor, none of my math classes have been too difficult.

\noindent
I feel that I have made the most out of my time here, but if I could go back to when I was first applying for college, I would have definitely aimed elsewhere. While there are certainly people here who take their academic studies seriously, I get the general vibe that many people here, students and professors alike, aren't really trying to excell in what they do. I want to stress that I don't hold this against anyone, I just wonder if I could have achieved more if I had gone somewhere more academically focused.

\end{document}
